Capturing the geometric structure of our experiences and how we remember them

### 2018-07-24 main.tex
checking in last topic model para

Then, we took a closer look at the themes contained in the top/bottom 3 events. We used the "memorability" weights described above to select the top/bottom events. We performed the same analysis as described above, but separately for the video event and average recall event vectors representing each of the top/bottom 3 remembered events. In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events. Each of the smaller colored dots represents the distribution of individual recall events over participants, colored by the closest video event.

>>>>

Then, we took a closer look at the themes contained in the top/bottom 3 events. We used the "memorability" weights to select the top/bottom events. We performed the same analysis as described above, but separately for the video event and average recall event vectors representing each of the top/bottom 3 remembered events. In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events. The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event. We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle. Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}b) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}c). These analyses uncover the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
